Who Stays Single? Exploring the Factors Behind Non-Marriage in the United States in 2023

### 2024-12-03 paper/paper.qmd
fix the sentences

Higher education levels were strongly associated with lower non-marriage rates. For instance, Figure @fig-edu-marriage shows that only 16% of individuals with education above a bachelor’s degree were unmarried, compared to 32% for those with "Some College" education. Logistic regression coefficients further underscore this trend, with individuals holding higher degrees being substantially less likely to remain unmarried (e.g., the coefficient for "Below High School" = 0.48). Education thus acts as a stabilizing factor, equipping individuals with economic resources and social networks conducive to marriage.

@@

Education emerged as the most significant predictor in this analysis. Higher education levels correlate strongly with lower non-marriage rates, as depicted in @fig-edu-marriage and @fig-coefficient. These findings align with theories suggesting that education enhances economic stability, expands social capital, and provides greater agency in life choices, all of which promote marriage. However, as @fig-income-distribution indicates, financial stability remains an essential but secondary factor in marital decisions.

@@

The table [@tbl-cleaned-data] shows the analysis data after data cleaning.

>>>>

Higher education levels were strongly associated with lower non-marriage rates. For instance, @fig-edu-marriage shows that only 16% of individuals with education above a bachelor’s degree were unmarried, compared to 32% for those with "Some College" education. Logistic regression coefficients further underscore this trend, with individuals holding higher degrees being substantially less likely to remain unmarried (e.g., the coefficient for "Below High School" = 0.48). Education thus acts as a stabilizing factor, equipping individuals with economic resources and social networks conducive to marriage.

@@

Education emerged as the most significant predictor in this analysis. Higher education levels correlate strongly with lower non-marriage rates, as depicted in @fig-edu-marriage and @fig-coefficient. These findings align with theories suggesting that education enhances economic stability, expands social capital, and provides greater agency in life choices, all of which promote marriage. However, as @fig-Income-Unmarried indicates, financial stability remains an essential but secondary factor in marital decisions.

@@

The @tbl-cleaned-data shows the analysis data after data cleaning.
